An Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis

### 2021-08-31 paper/paper.tex
add intro, start dataset section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{cite}
\def\typeofarticle{Article type} \def\currentvolume{1} \def\currentissue{1}
\def\currentyear{2021} \def\currentmonth{} \def\ppages{1--30} \def\DOI{to
appear} \def\Received{June 2022} \def\Accepted{July 2022} \def\Published{October
2022 }

\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

%\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}

\begin{document}

\title{Title of the paper}

\author{%
  Noah Gardner\affil{1} and Chih-Cheng Hung\affil{1}\corrauth}

@@

\address{%
  \addr{\affilnum{1}}{College of Computing and Software Engineering, Kennesaw
    State University, 1000 Chastain Road, Kennesaw, GA 30144, USA; email}
  % \addr{\affilnum{2}}{Affiliation email}
}
% corresponding author
\corraddr{chung1@kennesaw.edu}

\editor{ First-name Last-name}

@@

\section{Introduction}

Submission of a manuscript implies that the work described has not been
published before, and not been under consideration for publishing anywhere else.
Your submission also means that the manuscript has been approved by all
co-authors with appropriate permission if required. The publisher will not be
held legally responsible should any dispute be raised for any reason. AIMS-ACI
is an OA publication published quarterly by AIMS Press in February, May, August,
and November. Publishing is currently free of charge. Readers can access all
published articles free of charge through the journal website
https://aimspress.com/journal/aci

\section{Layout and fonts}
The page size is A4 ($8.5 \times 11.0$ in or $21.59 \times 27.94$ cm). The
margin is set to moderate. Font for all text, except symbols and formulae,
should use Times New Roman. Article title is bold with a font size 16 and
aligned to the left. Authors are bold with a font size 12. Using Times New Roman
size 12 for the main text, including figure captions and table titles. However,
text size for contents in a table can be chosen from 8 to 12 to fit the table
within the width of the page.

\section{Headline and sub-headline}
The first-level headline is numbered and bold with a font size 12, and has a
space of 12 $pt$ before and after the headline. Each paragraph begins with an
indentation of 0.63 $cm$ (the same by using the Tab key once) in the first line.
A paragraph does not have a space before and after that paragraph.

\subsection{The second-level headline}
The second-level headline is numbered with a font size 12. The second-level
headline has a default space of 6 $pt$ before and after it.

\subsubsection{The third-level headline (if necessary)}
If really necessary, the third-level headline should be numbered and italicized
with a font size 12, indented by 0.63 $cm$ (the same by using the Tab key once).
The third-level headline has a default space of 6 $pt$ before and after it. Any
lower headline should be avoided.

\subsection{Footnotes}
Although not encouraged, footnotes can be used to provide additional information
for an informal reference that cannot be included in the reference list. A
footnote should be numbered and cannot contain any figure or table. Use font
size 8 for footnotes.

\section{Figures or images, captions, tables, table titles, and formulae}
\subsection{Figure/image and caption}
Leave a space of one line before and after a figure or an image, i.e., one line
between the main text and the top of the figure or image, and one line between
the bottom of the figure or image and the caption. The caption has a default
space of 12 $pt$ after it so the main text can continue below the caption. If no
text follows the figure caption, do not leave any space between the caption and
the next headline (the headline has a default space).

\begin{figure}[ht]
  \centering
  \vskip 0.2in
  %\includegraphics[width=0.85\textwidth]{{logo_new.pdf}}
  \vspace {12pt}
  \caption{ Insert the figure/image here}
  \label{fig:res}
\end{figure}

Figures should be numbered consecutively in the text. A figure can be referred
explicitly in the text as Figure~\ref{fig:res}, or implicitly at the end of a
sentence in parentheses (Fig. 1).

Use black and white graphic for line drawings. All lines should be at least 0.1
mm (0.3 $pt$) wide. Line drawings or scanned line drawings should have a
resolution at least 600 dpi. Images with a large volume should be properly
compressed within 1 MB each. Scanned images should be properly edited to balance
the volume size and clarity of the image.

Figure captions begin with \textbf{Figure x.} in bold, followed by the text. Do
not add a full stop at the end of the caption.

\subsection{Tables and table titles}
\begin{table}[H]
  \begin{center}
    \caption{Publication schedule for AIMS-ACI in 2022}
    \begin{tabular}{lll} \hline
      Issue        & Publishing date   & Submission deadline \\\hline
      First issue  & February 25, 2022 & January 15, 2022    \\
      Second issue & May 25, 2022      & April 15, 2022      \\
      Third issue  & August 25, 2022   & July 15, 2022       \\
      Fourth issue & November 25, 2022 & October 15, 2022    \\\hline
    \end{tabular}
    \label{table}
  \end{center}
\end{table}

Table title should be placed above the table, numbered consecutively, and
referred in the text like Table~\ref{table} or (Table~\ref{table}). There is no
space between the table and table title. Leave a space of one line above the
table title and one line below the bottom of the table. If a new first-level
headline follows the table immediately, do not leave the space below the table.

The font of the table title is size 12 but the font of the table contents can be
sizes 8 to 12 depending on the best fit for the table. Table title begins with
\textbf{Table x}. in bold, followed by the text. Do not add a full stop at the
end of the table title.

\subsection{Mathematical formulae}
Mathematical formulae should be numbered consecutively by placing the number in
parentheses like (1), one TAB space away from the right line. Mathematical
formulae should be typed using MS Word Equation or better using \emph{MathType}.
Use size 10--12 for the main characters and size 6--8 for subscripts or
superscripts. Leave a space of 6 $pt$ between two formula in separate lines.
Some examples are shown below.

\begin{equation}
  \lim_{x \mapsto a^+ }f\left ( x \right )= \pm \infty \qquad \text{or} \qquad \lim_{x \mapsto a^- }f\left ( x \right )= \pm \infty
  \label{equation1}
\end{equation}

\begin{equation}
  \lim_{x \mapsto \infty }f\left ( x \right )=  a \qquad \text{or} \qquad \lim_{x \mapsto -\infty}f\left ( x \right )=  b
  \label{equation2}
\end{equation}

To cite a formula in the text, use the number like Equation~(\ref{equation1}),
or Eq.~(\ref{equation2}), or alike.

\section{Submission, review, and decision}
In the first year, submission, review and decisions of manuscripts is conducted
through email communications. Please send your manuscript to one of the relevant
Editors-in-Chief by their email available on the journal Website. With the
increase in submissions from 2022, we would use the AIMS Editorial System to
handle the process of submission, review, and decisions.

Once a submission is received, the receiving Editor will pre-screen the article
for its suitability and quality for the journal. After passing this
pre-screening, the Editor may act as the “Academic Editor” or assign this
manuscript to another Editor from the Editorial Board as the “Academic Editor”to
handle the review of this paper, communicate with the authors on revisions, and
inform the final decision after consultation with the relevant Editor-in-Chief.

AIMS-ACI holds a high standard in peer review. A submitted manuscript should be
reviewed by at least three independent reviewers who are scholars and
knowledgeable of the area of research. Standard review forms are available for
reviewers but they could choose own appropriate way of reporting to the Academic
Editor.

\section{Reference style, citation, and cross-reference}
Test citation \cite{ward_phylogeny_2014}.

@@

\bibliographystyle{unsrt}
\bibliography{paper}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{cite}

\usepackage{hyperref}
\hypersetup{colorlinks=true}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

\def\typeofarticle{Research Article} \def\currentvolume{1} \def\currentissue{1}
\def\currentyear{2021} \def\currentmonth{} \def\ppages{1--30} \def\DOI{to
appear} \def\Received{June 2022} \def\Accepted{July 2022} \def\Published{October
2022 }
%\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{An Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis}

\author{%
  Noah Gardner\affil{1}, John Paul Hellenbrand\affil{2}, and Chih-Cheng
  Hung\affil{1}\corrauth}

@@

\address{%
  \addr{\affilnum{1}}{College of Computing and Software Engineering, Kennesaw
    State University, 1000 Chastain Road, Kennesaw, GA 30144, USA; email}
  \addr{\affilnum{2}}{College of Science and Mathematics, Kennesaw State
    University, 1000 Chastain Road, Kennesaw, GA 30144, USA; email}}
% corresponding author
\corraddr{chung1@kennesaw.edu}

\editor{First-name Last-name}

@@

\section{Introduction}
Insects compose half of biodiversity and rank among the most dominant organisms
in terrestrial ecosystems \cite{sheikh_diverse_2017}. A key factor for the
ecological success of insects is their exoskeleton, also known as cuticle. The
cuticle protects insects from predation, provides structural support, prevents
desiccation, and serves as a canvas for advertising visual and chemical signals
\cite{gullan_insects_2009}. Research has heavily focused on the macrostructures
and internal chemical components that make the exoskeleton functional and more
recent work is being done to understand the functional aspects of external
cuticle micro sculpturing \cite{muthukrishnan_insect_2020,
  gunderson_insect_1989, watson_diversity_2017}.

We examine ants (\textit{Formicidae}) as they display an extreme diversity of
cuticle micro sculpturing across all subfamilies. Sculpturing ranges from
parallel longitudinal ridges to deep oval impressions to erratic protuberances.
The sculpturing has arisen convergently and independently throughout ant’s
evolutionary history, which suggests some inherent function. Cuticle sculpturing
on ants may help increase strength and rigidness, resist abrasion, increase
internal and external surface area, resist microbial growth, and rear beneficial
anti-biotic producing bacteria \cite{johnson_effect_2011,
  bruckner_relationship_2017, currie_coevolved_2006}. These specific functions may
be associated with certain sculpturing types and the purpose of classification
is to group similar textures based on proposed function.

\section{Methods}

\subsection{Sculpture Identification Protocol}

\subsection{Dataset}
In order to classify the cuticle, we used ant head images sourced from AntWeb
\cite{antweb}. In general, the ant head images are centered in the image, facing
the front, and share a similar posture. However, some images may not be
centered, show the ant head in a different orientation, or may have a
drastically different resolution from the average image. Additionally, images
can vary in scale. Fortunately, each can have several scales available such that
the images' scales can be roughly similar.

Images were collected and classified by undergraduate students according to the
sculpturing identification protocol. Overall, there are a total of 2443 images
in the dataset. The class spread is shown in

\section{Experimental Results}

@@

\bibliography{paper}
\bibliographystyle{unsrt}
